Results

### 2025-04-04 notebooks/00_index.qmd
feat: Add smooth function to PSP and THEMIS data processing, update plot labels

```{julia}
using Speasy
using SPEDAS
using SPEDAS: ulabel
using DimensionalData
using GLMakie
# using CairoMakie
using Dates
using PartialFunctions
using Beforerr: _theme_legend

@@

psp_temp = SPEDAS.DataSet(
    "Temperature",
    [
        SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/TEMP"; labels=["SPI Proton"]),
        SpeasyProduct("PSP_FLD_L3_SQTN_RFS_V1V2/electron_core_temperature"; labels=["SQTN Electron core"]),
    ];
    ylabel=Temp_ylabel
)

tvars_psp = [
    tnorm_combine ∘ SpeasyProduct("PSP_FLD_L2_MAG_RTN_4_SA_PER_CYC/psp_fld_l2_mag_RTN_4_Sa_per_Cyc"; ylabel=B_ylabel, labels=B_labels),
    psp_n,
    SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN"; ylabel=V_ylabel, labels=V_labels),
    psp_temp,
]

@@

f = Figure(; size=(1200, 800))
add_title = false
legend = (; position=Top())
tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; add_title, legend)
tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; add_title, legend)
tplot(f[1, 3], tvars_themis, tmin_wind, tmax_wind; add_title, legend)
add_labels!(f[1, 1]; labels='1':'9', open="(a.")
add_labels!(f[1, 2]; labels='1':'9', open="(b.")
add_labels!(f[1, 3]; labels='1':'9', open="(c.")
f
```

>>>>

```{julia}
using Speasy
using SPEDAS
using SPEDAS: ulabel, smooth
using DimensionalData
using GLMakie
# using CairoMakie
using Dates
using PartialFunctions
using Beforerr: _theme_legend

@@

psp_temp = SPEDAS.DataSet(
    "Temperature",
    [
        SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/TEMP"; labels=["SPI Proton"]),
        smooth(30u"s") ∘ SpeasyProduct("PSP_FLD_L3_SQTN_RFS_V1V2/electron_core_temperature"; labels=["SQTN Electron core"]),
    ];
    ylabel=Temp_ylabel
)

tvars_psp = [
    smooth(30u"s") ∘ tnorm_combine ∘ SpeasyProduct("PSP_FLD_L2_MAG_RTN_4_SA_PER_CYC/psp_fld_l2_mag_RTN_4_Sa_per_Cyc"; ylabel=B_ylabel, labels=B_labels),
    psp_n,
    SpeasyProduct("PSP_SWP_SPI_SF00_L3_MOM/VEL_RTN_SUN"; ylabel=V_ylabel, labels=V_labels),
    psp_temp,
]

@@

f = Figure(; size=(1200, 800))
add_title = false
legend = (; position=Top())
tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; add_title, legend)
add_labels!(f[1, 1]; labels='1':'9', open="(a.")

tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; add_title, legend)
add_labels!(f[1, 2]; labels='1':'9', open="(b.")

tplot(f[1, 3], tvars_themis, tmin_wind, tmax_wind; add_title, legend)
add_labels!(f[1, 3]; labels='1':'9', open="(c.")
f
```
